Uniform sampling over the all territory without any cell

### 2024-06-25 No_cell.Rmd
Variance

  true_value <- integral2(f, 0, 1000, 0, 1000)$Q 
  est_value <- mean(est_MC)
  return(c(true_value, est_value))
}
```

@@

```{r}
true_vs_MC(n = 10000, B = 10000, f = fun_norm)
# 1.000000 
```

>>>>

  true_value <- integral2(f, 0, 1000, 0, 1000)$Q # Theoretical value
  est_value <- mean(est_MC) # Estimated value
  return(c(true_value, est_value))
}
```

@@

```{r}
true_vs_MC(n = 10000, B = 10000, f = fun_norm)
# 1.000000 3.353247
```

# Variance

Variance formula for the uniform case is based on the formula given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which can be simplified in this particular case.

## Back to simple cases

### Case of the area

```{r}
n <- 100 # Sample size
pi <- sum(rep((1/1000)*(1/1000), n))
```

```{r}
# New variable: rho1^2
random_points$carre <- (random_points$rho1)^2
est_carre <- sum((random_points$carre)/pi)
# est_carre = est_area # Logical since rho1 = carre = 1
```

```{r}
var_area <- est_carre/pi - (1/n)*(est_area^2)
# The empirical variance is null as expected
```

```{r}
# fun1(x,y)^2 = fun1(x,y)
varTH_area <- integral2(fun1, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun1, 0, 1000, 0, 1000)$Q^2)
# The theoretical variance is null as expected
# Since the total is equal to the area
```

```{r}
# var_est <- function(f){
#   random_points$carre <- (random_points$rho1)^2
#   est_carre <- sum((random_points$carre)/pi)
# }
```

### Case of the ratio

```{r}
# New variable: rho2^2
random_points$carre2 <- (random_points$rho2)^2
est_carre2 <- sum((random_points$carre2)/pi)
# The new total is: 16571726

var_ratio <- est_carre2/pi - (1/n)*(est_ratio^2)
# Huge empirical variance: 124714284077
```

```{r}
fun_ratio2 <- function(x,y){
  fun_ratio(x,y)^2
}
varTH_ratio <- integral2(fun_ratio2, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun_ratio, 0, 1000, 0, 1000)$Q^2)
# Doesn't work, I don't know why
```
